Inference methods comparison for the simplified Naomi model

### 2023-02-28 src/naomi-simple_compare/comparison.Rmd
Have a look at large MCMC in comparison

@@

```{r}
rhats <- bayesplot::rhat(tmbstan$mcmc)
ess_ratio <- bayesplot::neff_ratio(tmbstan$mcmc)
niter <- 4 * tmbstan_details$niter / tmbstan_details$nthin
ess <- ess_ratio * niter
```

>>>>

```{r}
rhats <- bayesplot::rhat(tmbstan$mcmc$stanfit)
ess_ratio <- bayesplot::neff_ratio(tmbstan$mcmc$stanfit)
niter <- 4 * tmbstan_details$niter / tmbstan_details$nthin
ess <- ess_ratio * niter
```

@@
